The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-07 manuscript/manuscript.Rnw
properly escape `FDR` in the primate specific discussion

We examined the expression of three primates, \human, \bonobo, and
\smonkey. The genes whose expressions are different on the primate
lineage in comparison to all other analyzed species are listed in
\cref{tab:primate_lineage_specific}. \textit{FSTL1} has significantly
higher expression in the primate lineage
(\cref{fig:fstl1_evolution_tree},
$\mathrm{FDR}=\Sexpr{pri.all.lin.spec["FSTL1","FDR"]}$), is implicated
in BMP signaling, and has previously been implicated in inflammation
and invasiveness
\cite{Mouillet.ea2015:expressionandpost-transcriptionalregulation}. Of
non-primates, \horse shows the highest expression
%
\Sexpr{gene.expression(species.name="equus caballus",gene="FSTL1",complete=TRUE)}, 
%
which is still lower than the lowest primate, \smonkey
%
(\Sexpr{gene.expression(species.name="ateles fusciceps",gene="FSTL1",complete=TRUE)}). 
%
No other genes were significantly differentially expressed on this
lineage by t-test.

>>>>

We examined the expression of three primates, \human, \bonobo, and
\smonkey. The genes whose expressions are different on the primate
lineage in comparison to all other analyzed species are listed in
\cref{tab:primate_lineage_specific}. \textit{FSTL1} has significantly
higher expression in the primate lineage
(\cref{fig:fstl1_evolution_tree},
$\mathrm{FDR}=\Sexpr{pri.all.lin.spec["FSTL1",`FDR`]}$), is implicated
in BMP signaling, and has previously been implicated in inflammation
and invasiveness
\cite{Mouillet.ea2015:expressionandpost-transcriptionalregulation}. Of
non-primates, \horse shows the highest expression
%
\Sexpr{gene.expression(species.name="equus caballus",gene="FSTL1",complete=TRUE)}, 
%
which is still lower than the lowest primate, \smonkey
%
(\Sexpr{gene.expression(species.name="ateles fusciceps",gene="FSTL1",complete=TRUE)}). 
%
No other genes were significantly differentially expressed on this
lineage by t-test.
